---
title: "Test-Implementation-Segment-A3-Specific"
author: "Sixtus Dakurah"
date: "07/01/2021"
header-includes:
  - \usepackage{soul}
output: pdf_document
---


```{r setup, include=FALSE}
rm(list = ls())
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```


Define the variables:

$B:$ Total amount available for disbursement.

$S_i, \hspace{0.25cm} i = 1, 2, ..., s:$ Denote segment $i$ with a total of $s$ segments.

$L:$ Loan amount (This will be an average value).

$P:$ The price variable.

\hrule
Step 1: Fit the logistic model for the given segment.
\vspace{0.2cm}
\hrule

The design matrix is of the form:

$X= \left[j, x_2, x_3\right]$ where $l =2:$ Price, $l=3:$ Loan Amount.

The model for predicting the probability of booking is of the form:

\begin{equation}
  \pi{(X, \beta)}= \left[ \sigma(z_i), ..., \sigma(z_m) \right]^\prime
\end{equation}

Where $\sigma(z_k) = \left[ 1 + exp\{-z_k\} \right]^{-1}$ and $z_k = x_{k}\beta$, $k=1, ..., m$ the number of examples.

An expressive form for $x_k\beta = \beta_0 + \beta_{2}x_{k, 2} + \beta_{3}x_{k, 3}$



We now build a logistic model using the data from segment 1


```{r}
# load data
my_data <- read_csv("data/clean_transformed_data_07_20.csv")
head(my_data)
data.sim <- my_data %>% mutate(y = case_when(y=="No" ~ 0, y=="Yes"~1)) %>%
  rename(x1 = Cluster, x2 = Price, x3 = Loan, x4 = Cost, x5 = Age, x6= Rating) %>% mutate(x1 = as.factor(x1))
my_data %>% group_by(Segment) %>% summarise(n = n(), mean = mean(Loan), max = max(Loan), min = min(Loan))
```



```{r}
segment1 <- "1"
data.sim <- data.sim %>% filter(x1 == segment1)
#glm.segment1.fit <- glm(y~x1 + x2 + x3 + I(x1*x2) + 
#I(x1*x3), data = data.segment1, family = binomial)
glm.segment1.fit <- glm(y~x2 + x5 + x6, data = data.sim, family = binomial)
summary(glm.segment1.fit)
```


Extract the coefficients:

```{r}
seg1.intercept <- ((glm.segment1.fit)$coefficients)[[1]]
coef2 <- ((glm.segment1.fit)$coefficients)[[2]]
coef3 <- 0#((glm.segment1.fit)$coefficients)[[3]]
coef4 <- ((glm.segment1.fit)$coefficients)[[3]]
coef5 <- ((glm.segment1.fit)$coefficients)[[4]]
#seg2.intercept <- seg1.intercept +  ((glm.segment1.fit)$coefficients)[[2]]
#seg3.intercept <- seg1.intercept +  ((glm.segment1.fit)$coefficients)[[3]]
#price.coef <- ((glm.segment1.fit)$coefficients)[[4]]
```



The fitted model has the form:

$\hat{\sigma}(z_k) = \left[ 1 + exp\{ - {z}_k \} \right]^{-1}$


$\pi(x_2, \hat{\beta}) = \left[ \hat{\sigma}(z_1), ..., \hat{\sigma}(z_k) \right]^\prime$

```{r}
# get the predictions
segment1.pred.probs <- predict(glm.segment1.fit, type = "response")
data.sim <- data.sim %>% 
  mutate(pred.probs = segment1.pred.probs, 
         pred.y = as.factor(ifelse(pred.probs > 0.5, 's', 'f')))
head(data.sim)
```

```{r}
table(data.sim$pred.y, data.sim$y)
```


\hrule
Step 2: We now optimize over the price variable.
\vspace{0.2cm}
\hrule

```{r}
# Compute the total amount available for disbursement
(B <- data.sim %>% filter(x1==segment1) %>% pull(x3) %>% mean()) # this will now be the average loan amount.0
```

Denote the profit as:

$\rho(x_2, x_4) = x_2 - x_4$ where the new variable $x_4$ is the cost of booking.

The expected profit is then given as:

\begin{equation}
  E\left[\rho(x_2, x_4)|x_2\right] = \sum_{k=1}^{m} \pi(x_{\{k,2\}}, \hat{\beta})\rho(x_{\{k,2\}}, x_{\{k,4\}})
\end{equation}

We also have the expected loan amount of the form:


\begin{equation}
  E\left[x_3|x_2\right] = \sum_{k=1}^{m} \pi(x_{\{k,2\}}, \hat{\beta})*x_{k, 3}
\end{equation}



**The optimization problem is now of the form:**

\begin{equation}
  argmin_{x_2}  E\left[\rho(x_2, x_4)|x_2\right] \hspace{1cm} s.t. \hspace{0.5cm} E\left[x_3|x_2\right] < B_{avg}
\end{equation}

\hrule

\textcolor{red}{\st{This optimization problem is not well-defined and a solution can not be obtained if we employ single-variable optimization.}}

\st{This will be feasible if we resort to vector-valued optimization in which case the $\{k\}$ in $(2)$ and $(3)$ will be mute.}
\st{But that too will not be useful in this context as we're not looking to optimize for all known price points.}
\vspace{0.2cm}
\hrule

\st{A modification that will make optimization feasible}

Let $\rho(x_{\{k, 2\}}, x_{\{k, 4\}}) =x_{\{k, 2\}} - x_{\{k, 4\}}$ be the profit for a randomly chosen price point.

The expected profit is now given as:

\begin{equation}
  E\left[\rho(x_{\{k, 2\}}, x_{\{k, 4\}})|x_{\{k, 2\}}\right] = \pi(x_{\{k,2\}}, \hat{\beta})\rho(x_{\{k,2\}}, x_{\{k,4\}})
\end{equation}

We also have the expected loan amount of the form:


\begin{equation}
  E\left[x_{\{k, 3\}}|x_{\{k, 2\}}\right] = \pi(x_{\{k,2\}}, \hat{\beta})*x_{k, 3}
\end{equation}

**We now have the optimization problem:**

\begin{equation}
  argmin_{x_{\{k,2\}}}  E\left[\rho(x_{\{k,2\}}, x_{\{k,4\}})|x_{\{k, 2\}}\right] \hspace{1cm} s.t. \hspace{0.5cm} E\left[x_{\{k, 3\}}|x_{\{k, 2\}}\right]  < B_{avg}
\end{equation}


The Lagrangian is of the form:

\begin{equation}
\label{eqn:langrangian}
  F(x_{k, 2}, \lambda) =   E\left[\rho(x_{\{k,2\}}, x_{\{k,4\}})|x_{\{k, 2\}}\right] - \lambda\left[ E\left[x_{\{k, 3\}}|x_{\{k, 2\}}\right]  - B_{avg} \right]
\end{equation}


For ease of manipulation let:

$f(x_{k, 2}) =   E\left[\rho(x_{\{k,2\}}, x_{\{k,4\}})|x_{\{k, 2\}}\right]$ and $c(x_{k, 2}) =  E\left[x_{\{k, 3\}}|x_{\{k, 2\}}\right]  - B_{avg}$


Using Newton's method, we have the following derivations:


Opt 1: Quadratic Taylor series expansion for some chosen starting values $x_{k, 2}^o, \lambda^o$:


\begin{equation}
\label{eqn:quad-taylor-series}
  F(x_{k, 2}, \lambda) \approx  F(x_{k, 2}^o, \lambda^o) + 
  (x_{k, 2} - x_{k, 2}^o) \left.\frac{\partial F}{\partial x_{k, 2}}\right\vert_0 + 
  (\lambda - \lambda^o) \left. \frac{\partial F}{\partial \lambda}\right\vert_0 + 
  \frac{1}{2}(x_{k, 2} - x_{k, 2}^o)^2 \left.\frac{\partial^2 F}{\partial x_{k, 2}^2}\right\vert_0 + 
  (x_{k, 2} - x_{k, 2}^o)*(\lambda - \lambda^o) \left.\frac{\partial^2 F}{\partial x_{k, 2} \partial \lambda }\right\vert_0
\end{equation}


Opt 2: Inserting (\ref{eqn:langrangian}) into (\ref{eqn:quad-taylor-series}), we have:

\begin{equation}
\label{eqn:quaratic-taylor-series-expansion}
  \begin{split}
  F(x_{k, 2}, \lambda) \approx  F(x_{k, 2}^o, \lambda^o) + 
  (x_{k, 2} - x_{k, 2}^o)\left\{ \left.\frac{\partial f}{\partial x_{k, 2}}\right\vert_0 - \lambda^o \left.\frac{\partial c}{\partial x_{k, 2}}\right\vert_0  \right\} - 
  (\lambda - \lambda^o) c(x_{k, 2}^o) + \\
  \frac{1}{2}(x_{k, 2} - x_{k, 2}^o)^2\left\{ \left.\frac{\partial^2 f}{\partial x_{k, 2}^2}\right\vert_0 - \lambda \left.\frac{\partial^2 c}{\partial x_{2, k}^2}\right\vert_0  \right\} - 
  (x_{k, 2} - x_{k, 2}^o)*(\lambda - \lambda^o) \left.\frac{\partial c}{\partial x_{k, 2}}\right\vert_0
  \end{split}
\end{equation}

Note: the last part, the derivative is w.r.t. only the $x_{k, 2}$, as that of $\lambda$ goes to 1.

Opt 3: That the maximum is achieved at $x_{k, 2}$  requires the necessary condition:


\begin{equation}
\label{eqn:optcond}
  \begin{split}
    \frac{\partial F}{\partial x_{k, 2}} = \left.\frac{\partial f}{\partial x_{k, 2}}\right\vert_0 + (x_{k, 2} - x_{k, 2}^o)\left\{ \left.\frac{\partial^2 f}{\partial x_{k, 2}^2}\right\vert_0 - \lambda \left.\frac{\partial^2 c}{\partial x_{2, k}^2}\right\vert_0 \right\} - \lambda \left.\frac{\partial c}{\partial x_{k, 2}}\right\vert_0 = 0
  \end{split}
\end{equation}


Opt 4: We now derive the gradient update rules

We can easily see that:

\begin{equation}
\label{eqn:xgradient}
  \begin{split}
    \Delta x_{k, 2} = \frac{ \left\{ \lambda \left.\frac{\partial c}{\partial x_{k, 2}}\right\vert_0 - \left.\frac{\partial f}{\partial x_{k, 2}}\right\vert_0 \right\} }{\left\{ \left.\frac{\partial^2 f}{\partial x_{k, 2}^2}\right\vert_0 - \lambda \left.\frac{\partial^2 c}{\partial x_{2, k}^2}\right\vert_0 \right\} }
  \end{split}
\end{equation}



Similarly for a first order expansion of the constraints, we can solve a new value of $\lambda$ as follows:


\begin{equation}
\label{eqn:cgradient}
  \begin{split}
    c(x_{k, 2} ) = c(x_{k, 2}^o) +  \Delta x_{k, 2}\left.\frac{\partial c}{\partial x_{k, 2} }\right\vert_{x_{k, 2}^o} = 0
  \end{split}
\end{equation}


If we put (\ref{eqn:xgradient}) into (\ref{eqn:cgradient}), we have the following value of $\lambda$:

\begin{equation}
\label{eqn:lambdagradient}
  \begin{split}
    \lambda = \frac{\left\{ \left.\frac{\partial f}{\partial x_{k, 2}}\right\vert_0 \right\}  }{\left\{ \left.\frac{\partial c}{\partial x_{k, 2}}\right\vert_0 \right\}} - 
    \frac{\left\{ \left.\frac{\partial^2 f}{\partial x_{k, 2}^2}\right\vert_0 - \lambda \left.\frac{\partial^2 c}{\partial x_{2, k}^2}\right\vert_0 \right\} * c(x_{k, 2}^o) }{\left\{ \left.\frac{\partial c}{\partial x_{k, 2}}\right\vert_0 \right\}^2}
  \end{split}
\end{equation}

Putting this into (\ref{eqn:xgradient}) will give final update rule.
\vspace{0.2cm}

\hrule
Step 3: Algorithm
\vspace{0.2cm}
\hrule

The individual components for (\ref{eqn:xgradient}) are derived as follows:

\begin{align}
\label{eqn:ind1}
\left\{ \left.\frac{\partial f}{\partial x_{k, 2}}\right\vert_0 \right\}& 
  \begin{aligned}[t]
      &= \left\{ \left.\frac{\partial \left[\pi(x_{\{k,2\}}, \hat{\beta})\rho(x_{\{k,2\}}, x_{\{k,4\}}) \right] }{\partial x_{k, 2}}\right\vert_0 \right\}\\ 
      &= \left\{ \left.\frac{\partial \left[\pi(x_{\{k,2\}}, \hat{\beta})\right]}{\partial x_{k, 2}} \rho(x_{\{k,2\}}, x_{\{k,4\}}) + \pi(x_{\{k,2\}}, \hat{\beta}) \frac{\partial \left[\rho(x_{\{k,2\}}, x_{\{k,4\}}) \right] }{\partial x_{k, 2}} \right\vert_0 \right\}\\
      &= \left\{ \left. \hat{\beta}_2 exp\{-z_k\}\left[\hat{\sigma}(z_k)\right]^2*\rho(x_{\{k,2\}}, x_{\{k,4\}}) + \pi(x_{\{k,2\}}, \hat{\beta})   \right\vert_0 \right\}
  \end{aligned}
\end{align}


\begin{align}
\label{eqn:ind2}
\left\{ \left.\frac{\partial^2 f}{\partial x_{k, 2}^2}\right\vert_0 \right\}& 
  \begin{aligned}[t]
      &= \left\{ \left.  \frac{\partial}{\partial x_{k, 2}} \left[ \hat{\beta}_2 exp\{-z_k\}\hat{\sigma}(z_k)*\rho(x_{\{k,2\}}, x_{\{k,4\}}) + \pi(x_{\{k,2\}}, \hat{\beta}) \right]   \right\vert_0 \right\}\\
      &= \left(-\hat{\beta}_2^2 exp\{ -z_k \} * \left[ \hat{\sigma}(z_k) \right]^2 +  2\hat{\beta}_2^2 \left[exp\{ -z_k \}\right]^2 * \left[ \hat{\sigma}(z_k) \right]^3\right)*\rho(x_{\{k,2\}}, x_{\{k,4\}}) + \\
      &+ \hat{\beta}_2 exp\{ -z_k \}\left[ \hat{\sigma}(z_k) \right]^2 + \hat{\beta}_2 exp\{ -z_k \}\left[\hat{\sigma}(z_k)\right]^2 \lvert_0\\
  \end{aligned}
\end{align}


\begin{align}
\label{eqn:ind3}
\left\{ \left.\frac{\partial c}{\partial x_{k, 2}}\right\vert_0 \right\}& 
  \begin{aligned}[t]
      &= \left\{ \left.\frac{\partial \left[  \left[ \pi(x_{\{k,2\}}, \hat{\beta})*x_{k, 3} \right]  - B \right] }{\partial x_{k, 2}}\right\vert_0 \right\}\\ 
      &= \left\{ \left.  \hat{\beta}_2 exp\{ -z_k \}\left[\pi(x_{\{k,2\}}, \hat{\beta})\right]^2*x_{k, 3} \right\vert_0 \right\}
  \end{aligned}
\end{align}

\begin{align}
\label{eqn:ind4}
\left\{ \left.\frac{\partial^2 c}{\partial x_{k, 2}^2}\right\vert_0 \right\}& 
  \begin{aligned}[t]
      &= \left\{ \left. \hat{\beta}_2 \frac{\partial exp\{ -z_k \} }{\partial x_{k, 2}} * \left[\pi(x_{\{k,2\}}, \hat{\beta})\right]^2 * x_{k, 3} + \hat{\beta}_2  exp\{ -z_k \} * \frac{\partial}{\partial x_{k, 2}} \left[\pi(x_{\{k,2\}}, \hat{\beta})\right]^2*x_{k, 3}  \right\vert_0 \right\}\\
      &= \left\{ \left. -\hat{\beta}_2^2 exp\{ -z_k \}  * \left[\pi(x_{\{k,2\}}, \hat{\beta})\right]^2 * x_{k, 3} + 2\hat{\beta}_2^2  exp\{ -2z_k \} * \left[\pi(x_{\{k,2\}}, \hat{\beta})\right]^3*x_{k, 3}  \right\vert_0 \right\}
  \end{aligned}
\end{align}

We can now optimize as follows:

\hrule
\hrule

\textbf{Input:} $\hat{\beta}^*_0, \hat{\beta}_2$ the estimated coefficients from the logistic model.

\textbf{Output:} $x_{\{k, 2\}}$ the optimized price variable.

-1 Initialize points $x_{\{k, 2\}}^o$ and $\lambda^o$.

-2 Whiles not (\ref{eqn:optcond}) do:

-\hspace{1cm} Compute (\ref{eqn:ind1}), (\ref{eqn:ind2}), (\ref{eqn:ind3}) and (\ref{eqn:ind4}).

-\hspace{1cm} Obtain a new $x_{\{k, 2\}}$ using (\ref{eqn:xgradient}) and (\ref{eqn:lambdagradient}).

\hrule
\hrule


\hrule
Step 4: Implementation
\vspace{0.2cm}
\hrule


```{r}
# Initialize the price variables for the three segments:
init.price <- 0#mean((data.sim %>% filter(x1==segment1))$x2)
init.loan <- median((data.sim %>% filter(x1==segment1))$x3)
init.age <- median((data.sim %>% filter(x1==segment1))$x5)
init.rating <- median((data.sim %>% filter(x1==segment1))$x6)
#x23 <- mean((data.sim %>% filter(x1=="s3"))$x2)
#x31 <- mean((data.sim %>% filter(x1=="s1"))$x3)
#x32 <- mean((data.sim %>% filter(x1=="s2"))$x3)
#x33 <- mean((data.sim %>% filter(x1=="s3"))$x3)
# Initialize the lambda
lambda <- 0.4
```


```{r}
K <- 20
loan_amount_vector <- c(B)
booking_cost <- mean((data.sim %>% filter(x1==segment1))$x4)
variables_vector <- c(1, init.price, init.loan, init.age, init.rating)
coefficients_vector <- c(seg1.intercept, coef2, coef3, coef4, coef5)
```

Define the price indexes

```{r}
INTR_INDEX = 1
PRICE_INDEX = 2
LAMT_INDEX = 3
```


Build the utility functions here

```{r}

# Function to compute the exponent of the linear form:
compute_exp_lin_form <- function(variables_vector, coefficients_vector){
  # compute the linear form
  ln.form <- variables_vector*coefficients_vector
  return(exp(-sum(ln.form)))
}

# Unit test
print(compute_exp_lin_form(variables_vector, coefficients_vector))
```



```{r}
# Function to compute the estimated predicted probabilities:
compute_sigma_hat <- function(variables_vector, coefficients_vector){
  # compute the linear form
  ln.form <- variables_vector*coefficients_vector
  return <- (1 + compute_exp_lin_form(variables_vector, coefficients_vector) )^(-1)
}
# Unit test
print(compute_sigma_hat(variables_vector, coefficients_vector))
```


```{r}
# Function to compute the 1st partial derivative of f w.r.t. the price: (15)
compute_first_pd_of_f <- function(booking_cost, variables_vector, coefficients_vector){
  # first compute sigma of z-k using (1)
  price_coefficient  = coefficients_vector[PRICE_INDEX] # it's assumed this is in the third place
  lin_form <- compute_exp_lin_form(variables_vector, coefficients_vector)
  sigma_value <- compute_sigma_hat(variables_vector, coefficients_vector)
  # Implement the equation corresponding to (15)
  return_value <- (price_coefficient*lin_form*(sigma_value^2)*
                     (variables_vector[PRICE_INDEX] - booking_cost)) + sigma_value
  #print(variables_vector)
  #print(paste("New First PD of f in CFPDF: ", return_value))
  return(return_value)
}
compute_first_pd_of_f(booking_cost, variables_vector, coefficients_vector)
```


```{r}
# Function to compute the 2nd partial derivative of f w.r.t. the price: (16)
compute_second_pd_of_f <- function(booking_cost, variables_vector, coefficients_vector){
  # first compute sigma of z-k using (1)
  price_coefficient  = coefficients_vector[PRICE_INDEX] # it's assumed this is in the third place
  lin_form <- compute_exp_lin_form(variables_vector, coefficients_vector)
  sigma_value <- compute_sigma_hat(variables_vector, coefficients_vector)
  # Implement the equation corresponding to (16)
  first_half <- ( ((-price_coefficient^2)*lin_form*sigma_value^2) + 
                    (2*(price_coefficient^2)*(lin_form^2)*(sigma_value^3)) 
                  )*(variables_vector[PRICE_INDEX] - booking_cost)
  second_half <- (price_coefficient*lin_form*sigma_value^2
                  )+(price_coefficient*lin_form*(sigma_value^2))

  return_value <- first_half + second_half
  #print(paste("New Second PD of f in CSPDF: ", return_value))
  return(return_value)
}

# Function to compute the 1st partial derivative of c w.r.t. the price: (17)
compute_first_pd_of_c <- function(loan_amount_vector, variables_vector, 
                                  coefficients_vector){
  # Note: Loan amount will now simply contain a single item.
  # first compute sigma of z-k using (1)
  price_coefficient  = coefficients_vector[PRICE_INDEX] # it's assumed this is in the third place
  # first do for segment 1
  var_vec1 = variables_vector
  lin_f1 <- compute_exp_lin_form(var_vec1, coefficients_vector)
  sigma_v1 <- compute_sigma_hat(var_vec1, coefficients_vector)
  seg <- (price_coefficient*lin_f1*(sigma_v1)^2)*loan_amount_vector[1]
  
  return_value <- seg
  #print(paste("New PD of C in CFPDC: ", return_value))
  return(return_value)
}

# Function to compute the 1st partial derivative of c w.r.t. the price: (17)
compute_second_pd_of_c <- function(loan_amount_vector, variables_vector, 
                                  coefficients_vector){
  # first compute sigma of z-k using (1)
  price_coefficient  = coefficients_vector[PRICE_INDEX] # it's assumed this is in the third place
  # first do for segment 1
  var_vec1 = variables_vector
  lin_f1 <- compute_exp_lin_form(var_vec1, coefficients_vector)
  sigma_v1 <- compute_sigma_hat(var_vec1, coefficients_vector)
  seg <- (
    (-price_coefficient^2)*lin_f1*(sigma_v1)^2)*loan_amount_vector[1] + 
    ( 2*(price_coefficient^2)*(lin_f1^2)*(sigma_v1^2)*loan_amount_vector[1]  )
  return_value <- seg
  #print(paste("New PD of C in CFPDC: ", return_value))
  return(return_value)
}

compute_c <- function(loan_amount_vector, variables_vector, coefficients_vector, B){
  # first compute sigma of z-k using (1)
  price_coefficient  = coefficients_vector[PRICE_INDEX] # it's assumed this is in the third place
  # first do for segment 1
  var_vec1 = variables_vector
  sigma_v1 <- compute_sigma_hat(var_vec1, coefficients_vector)
  seg <- (sigma_v1)*loan_amount_vector[1]
  
  # Implement the equation corresponding to (15)
  return_value <- seg
  #print(variables_vector)
  #print(paste("Computed C in CC: ", return_value))
  return(return_value)
}
```




```{r}
# Function to compute the new lambda
compute_new_lambda <- function(loan_amount_vector, booking_cost, 
                               variables_vector, coefficients_vector, B){
  price_var = variables_vector[PRICE_INDEX]
  first_half = ( 
    compute_first_pd_of_f(
    booking_cost, variables_vector,coefficients_vector
    ) )/compute_first_pd_of_c(loan_amount_vector, variables_vector, coefficients_vector)
  second_half = ( 
    ( 
      compute_second_pd_of_f(
      booking_cost, variables_vector, coefficients_vector
      ) - compute_second_pd_of_c(loan_amount_vector, variables_vector, coefficients_vector) 
    )*compute_c(
        loan_amount_vector, variables_vector, coefficients_vector, B
        ) )/( 
          compute_first_pd_of_c(loan_amount_vector, variables_vector, coefficients_vector
                                )^2)
  return_value = first_half - second_half
  #print(paste("New Lambda in CNL: ", return_value))
  return(return_value)
}
# Function to compute the new price
compute_new_price <- function(
  lambda, loan_amount_vector, booking_cost, variables_vector, coefficients_vector
  ){
  price_var = variables_vector[PRICE_INDEX]
  first_half=( 
  lambda*compute_first_pd_of_c(loan_amount_vector, variables_vector, coefficients_vector) 
    ) - compute_first_pd_of_f(booking_cost, variables_vector, coefficients_vector)
  #print(paste("First Half in CNP: ", first_half))
  second_half=compute_second_pd_of_f(booking_cost, variables_vector, coefficients_vector) - 
    (lambda * compute_second_pd_of_c(loan_amount_vector, variables_vector, 
                                  coefficients_vector) )
  #print(paste("Second Half in CNP: ", second_half))
  return_value = (first_half/second_half) #+ price_var
  #print(variables_vector)
  #print(paste("New Price in CNP: ", return_value))
  return(return_value)
}

# Function to check if the minimum has been achieved: (11)
check_convergence <- function(new_price, lambda, loan_amount_vector, booking_cost, variables_vector, coefficients_vector){
  price_var = variables_vector[PRICE_INDEX]
  first_half = - ( 
  lambda*compute_first_pd_of_c(loan_amount_vector, variables_vector, coefficients_vector) 
    ) + compute_first_pd_of_f(booking_cost, variables_vector, coefficients_vector)
  #print(paste("First Half in CNP: ", first_half))
  second_half=compute_second_pd_of_f(booking_cost, variables_vector, coefficients_vector) - 
    (lambda * compute_second_pd_of_c(loan_amount_vector, variables_vector, 
                                  coefficients_vector) )
  #print(paste("Second Half in CNP: ", second_half)
  return_value = (first_half) + (new_price-price_var)*second_half
  return(return_value)
}
```



```{r}
# Loop to obtain the new values
data_values_s1 <- data.frame(index = c(1), lambda = c(1), price = c(1), conv = c(1), secp = c(1))
#data_values_s2 <- data.frame(index = c(1), lambda = c(1), price = c(1), conv = c(1), secp = c(1))
#data_values_s3 <- data.frame(index = c(1), lambda = c(1), price = c(1), conv = c(1), secp = c(1))

for (k in 1:K){
    
    new_lambda <- compute_new_lambda(loan_amount_vector, booking_cost, 
                                 variables_vector, coefficients_vector, B)
    new_x_value <- compute_new_price(new_lambda, loan_amount_vector, booking_cost, variables_vector, coefficients_vector)
    conv_value <- check_convergence(new_x_value, lambda, loan_amount_vector, booking_cost, variables_vector, coefficients_vector)
    sec_p_of_f <- compute_second_pd_of_f(booking_cost, variables_vector, coefficients_vector)
    # update the vectors
    variables_vector[PRICE_INDEX] <- new_x_value;
    data_values_s1[k, ] <- c(k, new_lambda, new_x_value, abs(conv_value), sec_p_of_f)
}
```



```{r}
data_values_s1 <- data_values_s1 %>% mutate(segment = factor(rep(segment1, K)))
data_values_s1
write_csv(data_values_s1, file = "data/opttimized_segment_S2_data_07_20.csv")
#data_values_s2 <- data_values_s2 %>% mutate(segment = factor(rep(2, K)))
#data_values_s3 <- data_values_s3 %>% mutate(segment = factor(rep(3, K)))
#head(data_values_s1)
```



```{r}
#library(ggplot2)
ggplot(data = data_values_s1) + geom_line(aes(x = index, y = price, color = segment)) 
```


```{r}
#ggplot(data = merged_data_values) + geom_line(aes(x = index, y = lambda, color = segment))
```



```{r}
#ggplot(data = merged_data_values) + geom_line(aes(x = index, y = secp, color = segment))
```













